COG-ED Manuscript

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
included effect size and CI for H1a

  knitr::opts_chunk$set(out.width = "\\textwidth")
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  #library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package

@@

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher n-back level.
Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not.
The specification curve analysis showed that this pattern was true for all 63 pipelines.
And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
All results are detailed in the *Supplementary Material*.

@@

This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

@@

\includepdf[pages={-}]{Design_Table_T1.pdf}

@@

`r apa_print(hypothesis1a_rmanova)$full_result`

>>>>

  knitr::opts_chunk$set(out.width = "\\textwidth")
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  #library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package
  library(effectsize)   # for effect sizes and CIs, "effectsize" package

@@

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher n-back level.
Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not.
The specification curve analysis showed that this pattern was true for all 63 pipelines.
And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
All results are detailed in the Supplementary Material.

@@

This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
**OR**
The authors received no specific funding for this work.

@@

(Starts on next page)

\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}

@@

`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI [`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`]
